
\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{tabularx}

\definecolor{sectionblue}{HTML}{1F6FB2}
\titleformat{\section}{\large\bfseries\color{sectionblue}}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{8pt}{4pt}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=2pt}

\begin{document}

\begin{center}
{\LARGE \textbf{ Ahmed Abdelrahman }} \\[4pt]
\href{Cairo, Egypt (UTC+3)}{Cairo, Egypt (UTC+3)} \textbar{} \href{+201024180920}{+201024180920} \textbar{} \href{ahmedabdelrhaman232@gmail.com}{ahmedabdelrhaman232@gmail.com} \textbar{} \href{https://www.linkedin.com/in/ahmed-abdelrahman-89bbb3203/}{https://www.linkedin.com/in/ahmed-abdelrahman-89bbb3203/} \textbar{} \href{https://kennycandra.dev}{https://kennycandra.dev}
\end{center}

\section{Skills}
\begin{tabularx}{\textwidth}{X X X}
\textbf{languages}\newline TypeScript, Rust, Python & \textbf{frontend}\newline React, Next.js, Tailwind CSS & \textbf{backend}\newline Node.js, Express.js, REST APIs, Event-Driven Architecture \\
\textbf{databases}\newline PostgreSQL, MongoDB, Redis & \textbf{infrastructure}\newline AWS (ECS Fargate, ECR, RDS, ElastiCache, Lambda, SSM), Docker, GitHub Actions CI/CD, Vercel & \textbf{core}\newline Distributed Systems, System Design, Database Internals, Clean Code \& Scalability \\
\end{tabularx}

\section{Education}
\textbf{Faculty of Pharmacy} \hfill 2024 \
Modern University, Cairo, Egypt

\section{Work Experience}
\textbf{Vogel Edits} \hfill 01/2025 - Present \\
\textit{Full-Stack Engineer (Adobe Extensions)}\\\begin{itemize}
\item Built and shipped production Adobe After Effects \& Premiere Pro extensions, including Vanish BG — a real-time AI background removal tool available at aescripts.com, running ML inference inside a sandboxed CEP environment.
\item Designed a Node.js sidecar process architecture to handle AI inference outside Adobe's restricted CEP sandbox, using local HTTP for IPC and streaming results back to the React UI in real time.
\item Built a TTS Premiere Pro extension using Node.js with local ONNX model inference, designing the full audio pipeline from text input to rendered timeline clip.
\item Collaborated asynchronously with designers and stakeholders, shipping production-ready tools using agile workflows.
\end{itemize}

\textbf{Freelance} \hfill 11/2024 - 01/2025 \\
\textit{Full-Stack Engineer}\\\begin{itemize}
\item Built a full-stack tourism booking platform using Next.js, TypeScript, and Node.js with TypeORM for type-safe PostgreSQL access.
\item Applied PostgreSQL indexing strategies and EXPLAIN ANALYZE to achieve sub-100ms API response times under concurrent load.
\item Integrated Paymob payment gateway with idempotent transaction handling and webhook verification, reducing checkout friction by 40\%.
\item Improved SEO and Core Web Vitals to 95+ Lighthouse score using Next.js SSR, image optimization, and lazy loading.
\end{itemize}

\section{Projects}
\textbf{RootCluster — AI-Powered Log Analysis Platform} \href{https://rootcluster.dev}{https://rootcluster.dev}\\
\textit{Tech Stack:} TypeScript, Node.js, PostgreSQL, Redis, AWS, Docker, BullMQ\\
\begin{itemize}
\item Designed and deployed a distributed log ingestion pipeline on AWS ECS Fargate processing 1M+ events/hour with sub-second latency.
\item Reduced ONNX embedding time from 20+ minutes to under 1 minute via batch processing, Redis caching, and worker autoscaling.
\item Designed an event-driven pipeline — normalize, embed, cluster, merge, root cause — with retries, exponential backoff, DLQs, and idempotent processing.
\item Set up full CI/CD with GitHub Actions OIDC, ECR, SSM Parameter Store, RDS PostgreSQL, and ElastiCache.
\item Applied PostgreSQL internals (indexing, MVCC, isolation levels) to build a high-throughput write pipeline avoiding lock contention.
\end{itemize}

\textbf{Medical CRM — AI-Enhanced Prescription Platform}\\
\textit{Tech Stack:} React, Node.js, PostgreSQL, JWT, RBAC\\
\begin{itemize}
\item Built a full-stack CRM handling diagnoses, prescriptions, and patient records with React, Node.js, and PostgreSQL.
\item Implemented JWT auth with access/refresh token rotation and RBAC across three permission levels.
\item Designed drug interaction validation across 500+ medications using graph-based PostgreSQL lookup.
\item Optimized dashboard queries for 10K+ monthly records using composite indexes and window functions.
\end{itemize}

\end{document}
