\documentclass[10pt, a4paper]{article}

% ─── Encoding & Fonts ─────────────────────────────────
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=0.6in, top=0.5in, bottom=0.5in]{geometry}

% ─── Packages ──────────────────────────────────────────
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{parskip}

% ─── Colors ────────────────────────────────────────────
\definecolor{primary}{HTML}{2B3A67}
\definecolor{accent}{HTML}{3B82F6}
\definecolor{subtle}{HTML}{6B7280}
\definecolor{divider}{HTML}{D1D5DB}

% ─── Section Styling ──────────────────────────────────
\titleformat{\section}
  {\large\bfseries\color{primary}\scshape}
  {}{0em}{}
  [\color{divider}\titlerule]
\titlespacing*{\section}{0pt}{10pt}{5pt}

% ─── List Styling ──────────────────────────────────────
\setlist[itemize]{
  leftmargin=1.2em,
  noitemsep,
  topsep=2pt,
  label=\textcolor{accent}{\textbullet}
}

% ─── No page numbers ──────────────────────────────────
\pagestyle{empty}

% ─── Custom Commands ──────────────────────────────────
\newcommand{\experienceheader}[3]{%
  \vspace{4pt}%
  {\textbf{#1} \hfill \textcolor{subtle}{\small #2}}\\
  {\textit{\textcolor{subtle}{#3}}}%
  \vspace{2pt}%
}

\begin{document}

% ─── Header ────────────────────────────────────────────
\begin{center}
  {\LARGE\bfseries\color{primary} Ahmed Abdelrahman}\\[6pt]
  {\small\color{subtle} \href{Cairo, Egypt (UTC+3)}{Cairo, Egypt (UTC+3)} \;\textcolor{divider}{\textbar{}}\; \href{+201024180920}{+201024180920} \;\textcolor{divider}{\textbar{}}\; \href{ahmedabdelrhaman232@gmail.com}{ahmedabdelrhaman232@gmail.com} \;\textcolor{divider}{\textbar{}}\; \href{https://www.linkedin.com/in/ahmed-abdelrahman-89bbb3203/}{https://www.linkedin.com/in/ahmed-abdelrahman-89bbb3203/} \;\textcolor{divider}{\textbar{}}\; \href{https://kennycandra.dev}{https://kennycandra.dev}}
\end{center}

\vspace{-4pt}

% ─── Skills ────────────────────────────────────────────
\section{Technical Skills}
\begin{tabularx}{\textwidth}{X X X}
\textbf{Languages}\newline TypeScript, Python & \textbf{Frontend}\newline React, Next.js, Tailwind CSS & \textbf{Backend}\newline Node.js, Express.js, REST APIs, Event-Driven Architecture, Async Processing \\[4pt]
\textbf{Databases}\newline PostgreSQL, Redis, MongoDB & \textbf{Async \& Messaging}\newline BullMQ, Dead-Letter Queues, Idempotent Processing & \textbf{Infrastructure}\newline AWS, Docker, GitHub Actions CI/CD, Vercel, DigitalOcean \\[4pt]
\end{tabularx}

% ─── Experience ────────────────────────────────────────
\section{Work Experience}
\textbf{Vogel Edits} \hfill {\small\textcolor{subtle}{01/2025 - Present}} \\
{\textit{\textcolor{subtle}{Full-Stack Engineer (Adobe Extensions)}}}\\\begin{itemize}
\item Shipped production Adobe After Effects \& Premiere Pro extensions with \textbf{React} UI and \textbf{Node.js} tooling, including Vanish BG (real-time AI background removal) published on https://aescripts.com.
\item Designed a \textbf{Node.js} sidecar architecture to bypass Adobe CEP sandbox limits, using local HTTP IPC to stream inference outputs to the UI in real time.
\item Implemented local model inference workflows (\textbf{ONNX}) and integrated them into user-facing editing pipelines with low-latency feedback loops.
\item Collaborated asynchronously with designers and stakeholders, delivering production-ready features with clear ownership and iterative releases.
\end{itemize}

\textbf{Freelance} \hfill {\small\textcolor{subtle}{11/2024 - 01/2025}} \\
{\textit{\textcolor{subtle}{Full-Stack Engineer}}}\\\begin{itemize}
\item Built a full-stack tourism booking platform using \textbf{Next.js}, \textbf{TypeScript}, and \textbf{Node.js} with type-safe \textbf{PostgreSQL} access via TypeORM.
\item Improved backend performance using \textbf{PostgreSQL} indexing and \textbf{EXPLAIN ANALYZE}, achieving sub-100ms API response times under concurrent load.
\item Integrated Paymob payments with \textbf{idempotent} transaction handling and secure webhook verification, reducing checkout friction by 40\%.
\item Raised SEO and Core Web Vitals to 95+ Lighthouse via \textbf{Next.js} SSR, image optimization, and lazy loading.
\end{itemize}

% ─── Projects ──────────────────────────────────────────
\section{Projects}
\textbf{RootCluster — AI-Powered Log Analysis Platform} \href{https://rootcluster.dev}{https://rootcluster.dev}\\
\textit{Tech Stack:} Node.js, TypeScript, PostgreSQL (pgvector), Redis, BullMQ, ONNX, AWS ECS Fargate, Docker, GitHub Actions\\
\begin{itemize}
\item Designed and deployed a distributed, \textbf{event-driven} ingestion pipeline on \textbf{AWS ECS Fargate} using \textbf{BullMQ} for job queuing, \textbf{Redis} for caching/rate limiting, and \textbf{PostgreSQL} (\textbf{pgvector}) for similarity search, processing 1M+ events/hour with sub-second latency.
\item Implemented robust \textbf{async processing} patterns: producer-consumer queues, worker pools with configurable concurrency, and priority routing for urgent vs. backfill workloads.
\item Built \textbf{dead-letter queues} with retry policies (exponential backoff, max attempts) to isolate malformed events without blocking the pipeline.
\item Designed \textbf{idempotent} processing with Redis-backed dedup keys and at-least-once delivery semantics via job completion callbacks.
\item Reduced \textbf{ONNX} embedding time from 20+ minutes to under 1 minute via batching, caching, and worker autoscaling.
\item Delivered CI/CD using \textbf{GitHub Actions} with AWS OIDC to ECR, plus RDS PostgreSQL, ElastiCache, SSM Parameter Store, and automated deployments.
\end{itemize}

\textbf{Medical CRM — AI-Enhanced Prescription Platform}\\
\textit{Tech Stack:} React, Node.js, PostgreSQL\\
\begin{itemize}
\item Built a full-stack CRM for diagnoses, prescriptions, and patient records with \textbf{React} and \textbf{Node.js} backed by \textbf{PostgreSQL}.
\item Implemented secure authentication with \textbf{JWT} access/refresh token rotation and \textbf{RBAC} across three permission levels.
\item Designed drug interaction validation across 500+ medications using graph-based \textbf{PostgreSQL} lookups.
\item Optimized dashboard queries for 10K+ monthly records using composite indexes and window functions.
\end{itemize}

\section{Coursework}
\begin{itemize}
\item Meta Certified Frontend Developer — Meta (2024)
\item Complete SQL Databases Bootcamp: Zero to Mastery — Udemy
\item Master the Coding Interview: Data Structures \& Algorithms — Udemy
\item Node.js: The Complete Guide — Udemy
\item Grokking Algorithms — Aditya Bhargava
\item Designing Data-Intensive Applications — Martin Kleppmann
\end{itemize}

\end{document}
