
\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{tabularx}

\definecolor{sectionblue}{HTML}{1F6FB2}
\titleformat{\section}{\large\bfseries\color{sectionblue}}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{8pt}{4pt}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=2pt}

\begin{document}

\begin{center}
{\LARGE \textbf{ Ahmed Abdelrahman }} \\[4pt]
\href{Cairo, Egypt (UTC+3)}{Cairo, Egypt (UTC+3)} \textbar{} \href{+201024180920}{+201024180920} \textbar{} \href{ahmedabdelrhaman232@gmail.com}{ahmedabdelrhaman232@gmail.com} \textbar{} \href{https://linkedin.com/in/ahmed-abdelrahman}{https://linkedin.com/in/ahmed-abdelrahman} \textbar{} \href{https://kennycandra.dev}{https://kennycandra.dev}
\end{center}

\section{Skills}
\begin{tabularx}{\textwidth}{X X X}
\textbf{languages}\newline TypeScript, JavaScript, Rust, Python & \textbf{frontend}\newline React, Next.js, Tailwind CSS, Redux & \textbf{backend}\newline Node.js, Express.js, REST APIs, Event-Driven Architecture, Async Processing, Software Design \\
\textbf{databases}\newline PostgreSQL (pgvector), MongoDB, MySQL, Redis (Caching \& Queues) & \textbf{asyncAndMessaging}\newline BullMQ, RabbitMQ, Dead-Letter Queues, Idempotent Processing, Exponential Backoff & \textbf{infrastructure}\newline AWS (ECS Fargate, ECR, RDS, ElastiCache, Lambda, SSM), Docker, GitHub Actions CI/CD, Vercel, DigitalOcean \\
\textbf{coreCompetencies}\newline Distributed Systems, System Design, CAP Theorem, MVCC, Database Internals, Networking (HTTP/2, HTTP/3, TCP/UDP, WebSockets) & \textbf{spoken}\newline English (Professional), Arabic (Native) &   \\
\end{tabularx}

\section{Education}
\textbf{Faculty of Pharmacy} \hfill 2024 \
Modern University, Cairo, Egypt

\section{Work Experience}
\textbf{Vogel Edits} \\
\textit{Full-Stack Engineer (Adobe Extensions)}\\\begin{itemize}
\item Delivered customer-facing AI extensions for Adobe After Effects \& Premiere Pro, including Vanish BG — a real-time background removal tool — serving as the technical bridge between ML capabilities and end-user production workflows.
\item Debugged and resolved Adobe's restricted CEP runtime limitations by designing a Node.js sidecar architecture that handles AI inference outside the sandbox, using local HTTP for IPC with real-time streaming.
\item Built and shipped a TTS Premiere Pro extension using Node.js with local ONNX model inference, owning the full pipeline from text input to rendered timeline clip.
\item Collaborated directly with designers and stakeholders in an async workflow, triaging customer issues and shipping production-ready tools on agile cycles.
\end{itemize}

\textbf{Freelance} \\
\textit{Full-Stack Engineer}\\\begin{itemize}
\item Built and integrated a full-stack tourism booking platform using Next.js, TypeScript, and Node.js — handling end-to-end implementation from customer-facing UI to backend APIs.
\item Diagnosed and resolved production performance bottlenecks using PostgreSQL EXPLAIN ANALYZE, achieving sub-100ms API response times under concurrent load.
\item Integrated Paymob payment gateway with idempotent transaction handling and webhook verification, reducing checkout friction by 40\% — directly analogous to enterprise third-party integrations.
\item Optimized Core Web Vitals to 95+ Lighthouse score, improving customer experience through SSR, image optimization, and lazy loading.
\end{itemize}

\section{Projects}
\textbf{RootCluster — AI-Powered Log Analysis Platform} \href{https://rootcluster.dev}{https://rootcluster.dev}\\
\textit{Tech Stack:} Node.js, TypeScript, PostgreSQL (pgvector), Redis, BullMQ, ONNX, AWS ECS Fargate, Docker, GitHub Actions\\
\begin{itemize}
\item Designed and deployed distributed log ingestion pipeline on AWS ECS Fargate processing 1M+ events/hour with sub-second latency.
\item Reduced ONNX embedding time from 20+ minutes to under 1 minute via batch processing, Redis caching, and worker autoscaling.
\item Designed event-driven pipeline: normalize → embed → cluster → merge → root cause, with retries, exponential backoff, DLQs, and idempotent processing.
\item Implemented centroid-based pgvector clustering to unify cross-service failures into single root causes.
\item Set up full CI/CD with GitHub Actions OIDC, ECR, SSM Parameter Store, RDS PostgreSQL, and ElastiCache.
\item Applied PostgreSQL internals (MVCC, isolation levels, indexing) to build high-throughput write pipeline avoiding lock contention.
\item Leveraged CAP theorem tradeoffs: PostgreSQL for strong consistency, Redis for high-availability caching.
\end{itemize}

\textbf{Medical CRM — AI-Enhanced Prescription Platform}\\
\textit{Tech Stack:} React, Node.js, PostgreSQL\\
\begin{itemize}
\item Built full-stack CRM handling diagnoses, prescriptions, and patient records for healthcare providers.
\item Implemented JWT auth with access/refresh token rotation and RBAC across three permission levels.
\item Designed drug interaction validation across 500+ medications using graph-based PostgreSQL lookup.
\item Optimized dashboard queries for 10K+ monthly records using composite indexes and window functions.
\end{itemize}

\end{document}
