
\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{tabularx}

\definecolor{sectionblue}{HTML}{1F6FB2}
\titleformat{\section}{\large\bfseries\color{sectionblue}}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{8pt}{4pt}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=2pt}

\begin{document}

\begin{center}
{\LARGE \textbf{ Ahmed Abdelrahman }} \\[4pt]
\href{Cairo, Egypt (UTC+3)}{Cairo, Egypt (UTC+3)} \textbar{} \href{+201024180920}{+201024180920} \textbar{} \href{ahmedabdelrhaman232@gmail.com}{ahmedabdelrhaman232@gmail.com} \textbar{} \href{https://www.linkedin.com/in/ahmed-abdelrahman-89bbb3203/}{https://www.linkedin.com/in/ahmed-abdelrahman-89bbb3203/} \textbar{} \href{https://kennycandra.dev}{https://kennycandra.dev}
\end{center}

\section{Skills}
\begin{tabularx}{\textwidth}{X X X}
\textbf{languages}\newline JavaScript, TypeScript, Go & \textbf{frontend}\newline React, Next.js, Tailwind CSS & \textbf{backend}\newline Node.js, Express.js, REST APIs, Event-Driven Architecture \\
\textbf{databases}\newline PostgreSQL, Redis & \textbf{architecture}\newline DDD, Hexagonal Architecture, Distributed Systems, Microservices & \textbf{infrastructure}\newline AWS (ECS Fargate, ECR, RDS, ElastiCache, Lambda, SSM), Docker, GitHub Actions CI/CD \\
\textbf{methodologies}\newline Agile, Product-Oriented Thinking, AI-Driven Engineering, CI/CD, Automated Testing &   &   \\
\end{tabularx}

\section{Education}
\textbf{} \hfill  \
Self-Taught Software Engineer

\section{Work Experience}
\textbf{Vogel Edits} \hfill 2025-01 - Present \\
\textit{Full-Stack Engineer (Adobe Extensions)}\\\begin{itemize}
\item Built and shipped production Adobe After Effects \& Premiere Pro extensions, including Vanish BG — a real-time AI background removal tool running ML inference inside a sandboxed CEP environment; published on aescripts.com.
\item Designed a Node.js sidecar process architecture that circumvents Adobe's restricted CEP runtime by handling AI inference externally, using local HTTP for IPC and streaming results back to the React UI in real time.
\item Built and submitted a TTS Premiere Pro extension using Node.js with local ONNX model inference, designing the full audio pipeline from text input to rendered timeline clip.
\item Collaborated asynchronously with designers and stakeholders in an agile workflow, shipping production-ready tools end-to-end.
\end{itemize}

\textbf{Freelance} \hfill 2024-11 - 2025-01 \\
\textit{Full-Stack Engineer}\\\begin{itemize}
\item Built a full-stack tourism booking platform using Next.js, TypeScript, and Node.js with TypeORM for type-safe PostgreSQL access — delivered autonomously from conception to deployment.
\item Applied PostgreSQL indexing strategies and EXPLAIN ANALYZE to achieve sub-100ms API response times under concurrent load.
\item Integrated Paymob payment gateway with idempotent transaction handling and webhook verification, reducing checkout friction by 40\%.
\item Improved SEO and Core Web Vitals to 95+ Lighthouse score using Next.js SSR, image optimization, and lazy loading.
\end{itemize}

\section{Projects}
\textbf{RootCluster — AI-Powered Log Analysis Platform} \href{https://rootcluster.dev}{https://rootcluster.dev}\\
Distributed log ingestion and root-cause analysis platform processing 1M+ events/hour with sub-second latency.\\
\textit{Tech Stack:} TypeScript, Node.js, PostgreSQL, Redis, AWS ECS Fargate, Docker, BullMQ\\
\begin{itemize}
\item Designed and deployed event-driven microservices pipeline on AWS ECS Fargate: normalize → embed → cluster → merge → root cause, with retries, exponential backoff, DLQs, and idempotent processing.
\item Reduced ONNX embedding time from 20+ minutes to under 1 minute via batch processing, Redis caching, and worker autoscaling.
\item Built full CI/CD pipeline with GitHub Actions OIDC, ECR, SSM Parameter Store, RDS PostgreSQL, and ElastiCache.
\item Applied CAP theorem tradeoffs — PostgreSQL for strong consistency, Redis for high-availability caching — and PostgreSQL internals (MVCC, isolation levels, indexing) for a high-throughput write pipeline.
\end{itemize}

\textbf{Medical CRM — AI-Enhanced Prescription Platform}\\
Full-stack CRM handling diagnoses, prescriptions, and patient records with drug interaction validation across 500+ medications.\\
\textit{Tech Stack:} React, Node.js, PostgreSQL, JWT, RBAC\\
\begin{itemize}
\item Built full-stack SPA with React and Node.js implementing JWT auth with access/refresh token rotation and RBAC across three permission levels.
\item Designed graph-based drug interaction lookup in PostgreSQL for sub-100ms validation across 500+ medications.
\item Optimized dashboard queries for 10K+ monthly records using composite indexes and window functions.
\end{itemize}

\end{document}
