\documentclass[10pt, a4paper]{article}

% ─── Encoding & Fonts ─────────────────────────────────
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=0.6in, top=0.5in, bottom=0.5in]{geometry}

% ─── Packages ──────────────────────────────────────────
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{parskip}

% ─── Colors ────────────────────────────────────────────
\definecolor{primary}{HTML}{2B3A67}
\definecolor{accent}{HTML}{3B82F6}
\definecolor{subtle}{HTML}{6B7280}
\definecolor{divider}{HTML}{D1D5DB}

% ─── Section Styling ──────────────────────────────────
\titleformat{\section}
  {\large\bfseries\color{primary}\scshape}
  {}{0em}{}
  [\color{divider}\titlerule]
\titlespacing*{\section}{0pt}{10pt}{5pt}

% ─── List Styling ──────────────────────────────────────
\setlist[itemize]{
  leftmargin=1.2em,
  noitemsep,
  topsep=2pt,
  label=\textcolor{accent}{\textbullet}
}

% ─── No page numbers ──────────────────────────────────
\pagestyle{empty}

% ─── Custom Commands ──────────────────────────────────
\newcommand{\experienceheader}[3]{%
  \vspace{4pt}%
  {\textbf{#1} \hfill \textcolor{subtle}{\small #2}}\\
  {\textit{\textcolor{subtle}{#3}}}%
  \vspace{2pt}%
}

\begin{document}

% ─── Header ────────────────────────────────────────────
\begin{center}
  {\LARGE\bfseries\color{primary} Ahmed Abdelrahman}\\[6pt]
  {\small\color{subtle} \href{Cairo, Egypt (UTC+3)}{Cairo, Egypt (UTC+3)} \;\textcolor{divider}{\textbar{}}\; \href{+201024180920}{+201024180920} \;\textcolor{divider}{\textbar{}}\; \href{ahmedabdelrhaman232@gmail.com}{ahmedabdelrhaman232@gmail.com} \;\textcolor{divider}{\textbar{}}\; \href{https://www.linkedin.com/in/ahmed-abdelrahman-89bbb3203/}{https://www.linkedin.com/in/ahmed-abdelrahman-89bbb3203/} \;\textcolor{divider}{\textbar{}}\; \href{https://kennycandra.dev}{https://kennycandra.dev}}
\end{center}

\vspace{-4pt}

% ─── Skills ────────────────────────────────────────────
\section{Technical Skills}
\begin{tabularx}{\textwidth}{X X X}
\textbf{Languages}\newline TypeScript, Rust, Python & \textbf{Backend}\newline Node.js, Express.js, REST APIs, Event-Driven Architecture, Async Processing & \textbf{Databases}\newline PostgreSQL, MongoDB, Redis \\[4pt]
\textbf{Async \& Messaging}\newline BullMQ, Dead-Letter Queues, Idempotent Processing & \textbf{Infrastructure}\newline Docker, GitHub Actions CI/CD, AWS ECS Fargate, DigitalOcean &   \\[4pt]
\end{tabularx}

% ─── Experience ────────────────────────────────────────
\section{Work Experience}
\textbf{Vogel Edits} \\
{\textit{\textcolor{subtle}{Full-Stack Engineer (Adobe Extensions)}}}\\\begin{itemize}
\item Architected a \textbf{Node.js} sidecar process to handle \textbf{AI inference} outside Adobe's sandboxed CEP runtime, enabling scalable \textbf{microservices} communication via local HTTP \textbf{API} for real-time results.
\item Designed and built \textbf{REST APIs} and background services for \textbf{ONNX} model inference, implementing \textbf{event-driven} patterns to decouple frontend UI from backend processing.
\item Implemented \textbf{caching} strategies and \textbf{async} processing pipelines to optimize performance of \textbf{AI-powered} tools across production Adobe extensions.
\end{itemize}

\textbf{Freelance} \\
{\textit{\textcolor{subtle}{Full-Stack Engineer}}}\\\begin{itemize}
\item Designed and built \textbf{REST APIs} using \textbf{Node.js} and \textbf{Express.js} with \textbf{TypeORM} for type-safe \textbf{PostgreSQL} access, delivering scalable backend services for a tourism booking platform.
\item Optimized \textbf{database} performance using \textbf{PostgreSQL} indexing strategies and \textbf{EXPLAIN ANALYZE} to achieve sub-100ms \textbf{API} response times under concurrent load.
\item Implemented secure payment \textbf{API} integration with idempotent transaction handling and webhook verification, reducing checkout friction by 40\%.
\end{itemize}

\textbf{RootCluster} \\
{\textit{\textcolor{subtle}{Backend Engineer}}}\\\begin{itemize}
\item Designed and deployed a distributed, \textbf{event-driven} log ingestion pipeline on \textbf{AWS ECS Fargate} using \textbf{BullMQ} for \textbf{job queuing}, \textbf{Redis} for \textbf{caching} and rate limiting, and \textbf{PostgreSQL} (pgvector) for similarity search — processing 1M+ events/hour with sub-second latency.
\item Implemented robust \textbf{async} processing patterns: producer-consumer queues for log normalization, \textbf{worker pools} with configurable concurrency, and \textbf{priority queues} for urgent events vs. batch backfill jobs.
\item Built \textbf{dead-letter queues} (\textbf{DLQs}) with retry policies (exponential backoff, max attempts) to handle malformed or failing log entries without pipeline blockage.
\item Designed \textbf{idempotent} event processing using \textbf{Redis}-backed dedup keys and at-least-once delivery semantics through BullQueue's job completion callbacks.
\item Reduced \textbf{ONNX} embedding time from 20+ minutes to under 1 minute via batch processing, \textbf{Redis} caching, and \textbf{worker autoscaling}.
\item Set up full \textbf{CI/CD} with \textbf{GitHub Actions} OIDC, \textbf{ECR}, \textbf{SSM Parameter Store}, \textbf{RDS PostgreSQL}, and \textbf{ElastiCache}.
\end{itemize}

\textbf{Medical CRM} \\
{\textit{\textcolor{subtle}{Full-Stack Engineer}}}\\\begin{itemize}
\item Designed and implemented \textbf{REST APIs} using \textbf{Node.js} and \textbf{Express.js} for a full-stack CRM handling diagnoses, prescriptions, and patient records.
\item Implemented \textbf{JWT} auth with access/refresh token rotation and \textbf{RBAC} across three permission levels, securing backend \textbf{API} endpoints.
\item Optimized \textbf{database} queries for 10K+ monthly records using composite indexes and \textbf{PostgreSQL} window functions.
\end{itemize}

% ─── Projects ──────────────────────────────────────────
\section{Projects}
\textbf{RootCluster — AI-Powered Log Analysis Platform} \href{rootcluster.dev}{rootcluster.dev}\\
\textit{Tech Stack:} Node.js, TypeScript, PostgreSQL (pgvector), Redis, BullMQ, ONNX, AWS ECS Fargate, Docker, GitHub Actions\\
\begin{itemize}
\item Designed and deployed a distributed, \textbf{event-driven} log ingestion pipeline on \textbf{AWS ECS Fargate} using \textbf{BullMQ} for \textbf{job queuing}, \textbf{Redis} for \textbf{caching} and rate limiting, and \textbf{PostgreSQL} (pgvector) for similarity search — processing 1M+ events/hour with sub-second latency.
\item Implemented robust \textbf{async} processing patterns: producer-consumer queues for log normalization, \textbf{worker pools} with configurable concurrency, and \textbf{priority queues} for urgent events vs. batch backfill jobs.
\item Built \textbf{dead-letter queues} (\textbf{DLQs}) with retry policies (exponential backoff, max attempts) to handle malformed or failing log entries without pipeline blockage.
\item Designed \textbf{idempotent} event processing using \textbf{Redis}-backed dedup keys and at-least-once delivery semantics through BullQueue's job completion callbacks.
\item Reduced \textbf{ONNX} embedding time from 20+ minutes to under 1 minute via batch processing, \textbf{Redis} caching, and \textbf{worker autoscaling}.
\item Implemented centroid-based \textbf{pgvector} clustering to unify cross-service failures into single root causes.
\item Set up full \textbf{CI/CD} with \textbf{GitHub Actions} OIDC, \textbf{ECR}, \textbf{SSM Parameter Store}, \textbf{RDS PostgreSQL}, and \textbf{ElastiCache}.
\end{itemize}

\textbf{Medical CRM — AI-Enhanced Prescription Platform}\\
\textit{Tech Stack:} React, Node.js, PostgreSQL\\
\begin{itemize}
\item Built full-stack CRM handling diagnoses, prescriptions, and patient records.
\item Implemented \textbf{JWT} auth with access/refresh token rotation and \textbf{RBAC} across three permission levels.
\item Designed drug interaction validation across 500+ medications using graph-based \textbf{PostgreSQL} lookup.
\item Optimized dashboard queries for 10K+ monthly records using composite indexes and window functions.
\end{itemize}

\section{Coursework}
\begin{itemize}
\item Meta Certified Frontend Developer — Meta (2024)
\item Complete SQL Databases Bootcamp: Zero to Mastery — Udemy
\item Master the Coding Interview: Data Structures \& Algorithms — Udemy
\item Node.js: The Complete Guide — Udemy
\item Grokking Algorithms — Aditya Bhargava
\item Designing Data-Intensive Applications — Martin Kleppmann
\end{itemize}

\end{document}
